6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-22 paper.tex
Slight abstract tweak

In this report, we discuss and implement an infrastructure modelling and monitoring tool that can be used to help manage some of the inherent complexity in modern infrastructure. We will attempt to design an infrastructure modelling language, and use this model to validate real-world systems, as well as generating helpful architecture diagrams for documentation purposes.

>>>>

In this report, we discuss and implement an infrastructure modelling and monitoring tool that can be used to help manage some of the inherent complexity in modern infrastructure. We will attempt to design an infrastructure modelling language, and use the subsequently produced models to effectively visualise and validate the correctness of real-world systems.
